Title of the Master Thesis

### 2015-10-01 Master Thesis/synopsis.tex
Finish synopsis

\section{Some results on $\operatorname{Spv}(K)$}

@@

\section{Local correspondence}

@@

>>>>

\section{Some Results on $\operatorname{Spv}(K)$}

@@

\section{Local Correspondence}

@@

\section{Global Correspondence mod $n$}

\begin{lemma}\label{4.1}
Let $E$ be a number field and let $X$ be a smooth projective geometrically connected curve over $E$. Let $\pi:X'\to X$ be a connected Galois covering of degree $d$ which splits completely, i.e. every closed point $P\in X_0$ has exactly $d$ pre-images in $X'$. Then $d=1$.
\end{lemma}

\paragraph{} Let $k$ and $k'$ be the algebraic closures of $\mathbb{Q}$ in $K$ and $K'$ respectively, and let $\overline{k}$ and $\overline{k'}$ be the algebraic closure of $k$ and $k'$ in $\overline{K}$ and $\overline{K'}$ respectively.

Let $X$ and $X'$ be the unique smooth projective curve over $k$ and $k'$ with function field $K$ and $K'$ respectively. We identify the set of closed points $X_0$ of $X$ with the set of valuations $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ with $\operatorname{char} k(v)=0$ and similarly identify $X'_0$ with the corresponding subset of $\operatorname{Spv}_\text{d}^{(1)}(K')$.

\begin{lemma}\label{4.2}
We have $(K\overline{k})'=K'\overline{k'}$, i.e. $\sigma(G_{K\overline{k}})=G_{K'\overline{k'}}$. $\sigma$ induces an isomorphism $G_k\to G_{k'}$ such that the following diagram commutes:
\[ \begin{tikzcd}
G_K \ar[r, "\sigma"] \ar[d, "\text{res}"'] & G_{K'}\ar[d, "\text{res}"]\\
G_k \ar[r, "\sigma"'] & G_{k'}
\end{tikzcd} \]
Moreover, $\sigma:G_k\to G_{k'}$ is induced by a unique isomorphism $\varphi:\overline{k'}\to\overline{k}$.
\end{lemma}

\begin{definition}\label{4.4}
For a finite subset $S\subset X_0$ set:
\[ K^S=\{x\in K^\times \mid v_P(x)=0\text{ for all }P\in X_0\setminus S \} \]
$K'^{S'}$ is defined similarly. For finite subsets $S$ of $X_0$, the corresponding subsets of $X_0'$ will be denoted by $S'$, i.e. $S'=\sigma(S)$.
\end{definition}

\begin{lemma}\label{4.5}
\begin{enumerate}[(i)]
\item There exists a finite subset $S\subset X_0$ such that:
\[ \operatorname{Pic}(X\setminus S)=0=\operatorname{Pic}(X'\setminus S') \]
Such a set $S$ is called \textit{admissible}. If $V\subset X$ is an open subscheme, then one can choose $S$ in $V_0$.
\item Let $S$ be admissible. For all $n\in\mathbb{N}$ the following canonical maps are injective:
\[ K^S/n \to K^\times /n,\quad K'^{S'}/n\to K'^\times /n \]
$\varphi_n$ induces isomorphisms $\varphi_n: K'^{S'}/n\to K^S/n$.
\end{enumerate}
\end{lemma}

\section{The Proof}

\begin{definition}\label{5.1}
An abelian group is called \textit{free-by-finite} if its torsion subgroup $A_\text{tor}$ is finite and the quotien $A/A_\text{tor}$ is free abelian. $A$ is free-by-finite if and only if $A$ is the direct sum of a finite group and a free abelian group.
\end{definition}

\begin{lemma}\label{5.2}
\begin{enumerate}[(i)]
\item Let $A\to B$ be a homomorphism of abelian groups with finite kernel and cokernel. Then $A$ is free-by-finite iff $B$ is free-by-finite.
\item Let $0\to A'\stackrel{i}{\to}A\stackrel{p}{\to}A''\to 0$ be an exact sequence of abelian groups. If $A'$ and $A''$ are free-by-finite, then $A$ is free-by-finite. Conversely, if $A$ is free-by-finite, then $A'$ is free-by-finite. If additionally, $A'$ is finitely generated, then $A''$ is free-by-finite.
\item Let $A$ be free-by-finite. Then $\bigcap_{n\in\mathbb{N}}nA=0$.
\end{enumerate}
\end{lemma}

\begin{lemma}\label{5.3}
Let $F$ be a number field. Then:
\begin{enumerate}[(i)]
\item $F^\times$ is free-by-finite.
\item Let $F_1,\ldots,F_n$ be finite extensions of $F$. Then $\prod_{i=1}^{n}F_i^\times/F^\times$ is free-by-finite, where $F^\times$ is considered as a subgroup of $\prod_{i=1}^{n}F_i^\times$ via the diagonal embedding.
\end{enumerate}
\end{lemma}

\begin{lemma}
Let $S\subset X_0$ be admissible. Then there exists a finite subset $T\subset X_0$ with $T\cap S=\varnothing$ such that the following map is injective:
\[ r_{S,T}:K^S \to\prod_{P\in T}k(P)^\times,\ x\mapsto(r_P(x))_{P\in T} \]
In this case, $\operatorname{coker}(r_{S,T})$ is free-by-finite.
\end{lemma}
